Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-17 paper.tex
update intro figure with archetype

\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
\centering
\fbox{
    \begin{minipage}{2in}
        \hfill\vspace{1in}
    \end{minipage}
    }
\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
\end{figure}

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office room procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
\emph{Augraphy} offers \numAugraphyAugmentations~ individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~X and in Figure~Y.
This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.

>>>>

%\begin{figure} % temp placeholder for figure... this figure should be compelling and help the reader understand what Augraphy is about
%\centering
%\fbox{
%    \begin{minipage}{2in}
%        \hfill\vspace{1in}
%    \end{minipage}
%    }
%\caption{Placeholder for compelling figure to help the reader understand what Augraphy is about.}   
%\end{figure}

\begin{figure}
    \centering\scalebox{0.475}{
    \includegraphics{figures/archetype-memo.pdf}}
    \caption{\emph{Augraphy} can be used to introduce noisy perturbations to document images like the noise seen in (a), which is a real-life sample from  RVL-CDIP. We re-created a clean version of (a) in (b). We then create a noisy version of (b) by applying several augmentations to it to produce (c).}
    \label{fig:intro}
\end{figure}

For this reason we introduce \emph{Augraphy}, an open-source Python-based data augmentation library for generating versions of document images that contain realistic noise artefacts commonly introduced via scanning, photocopying, and other office room procedures.
\emph{Augraphy} differs from most image data augmentation tools by specifically targeting the types of alterations and degradations seen in document images.
\emph{Augraphy} offers \numAugraphyAugmentations ~individual augmentation methods out-of-the-box across three ``phases" of augmentations, and these individual phase augmentations can be composed together along with a where different paper backgrounds can be added to the augmented image.
The resulting document images are realistic, noisy versions of clean documents, as evidenced in Figure~\ref{fig:intro}, where we apply several \emph{Augraphy} augmentations to a clean document image in order to mimic the types of noise seen in a real-world noisy document image from RVL-CDIP.
This paper provides an overview of the \emph{Augraphy} library, and demonstrates how it can be used both as a training data augmentation tool and as an effective means for producing data for robustness testing.
